Foreign Exchange Speculation: An Event Study

### 2018-01-16 MDPI/MDPI_template/FinStudies.tex

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties with the need for large prices concessions.}. Speculators offer a service for a fee that is determined by the return on their activity.  \replaced{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.}{\citet{FriedmanPositive} argued that even where there are a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of teh market.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd'\added{. Uninformed speculators may dominate} and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constraint on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues to the current era where there has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  A common story that has encouraged congressional investigation says that wild speculation drove oil and other commodities prices well above their fundamental value causing harship for commodity consumers and a subsequent collapse that was equally disruptive for the producders.  \citet{PindyckSpec} show a broad movement of commodities prices not linked to fundaments that they argue is caused by speculation.  \citet{TangSpec} suggest that this speculative disruption was exacerbated by speculation on commodity indices.  However, \citet{ScottSpec} do not find a link between speculative positions and excess price movements in commodities.   \citet{Jacksspec} documents the history of attacks on speculation following price volatility.}

@@

\replaced{More recently the debate has move towards the way that noise-trading speculators may affect welfare and how that could be contained. \citet{Tobin1982} and \citet{Tobvin} developed the argument for the eponymous transaction tax that would seek to limit the influence of exchange rate speculation.  \citet{ERW} use a series of fundamentals to show how speculation casued unwarranted devaluations during the period of the European Exchange Rate Mechanism (ERM).   \citet{Tobin3} use this experience to re-state the call for a tax to reduce speculation.  However, if speculation is informed and part of the process of price discovery this tax can be counterproductive as it will reduce liquidity and may cause evengreater volatility. This is a point made by \citet{Mayer} and \citet{McKinnon}.

@@

\section{Measuring speculation}
\added{It is common practice to back market expectations out of information drawn from option prices.}  \footnote{If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review. }  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.

>>>>

\begin{document}
\section{Introduction}
\added{Speculation can be stabilising or destabilising.} If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} \deleted{for example} emphasise the role that speculation plays in facilitating financial market transactions \added{by providing liquidity that allows hedgers and other market participants to swiftly find counterparties without the need for large prices concessions.} Speculators offer a service for a fee that is determined by the return on their activity.  \replaced{\citet{FriedmanPositive} argued that even where there are a mixture of infomed and unnformed speculators, the informed woudl tend to buy when prices were below intrinsic value and sell when above, making profits, stabilising the market and driving the loss-making uninformed speculators out of business.}{While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.} \deleted{However, the later} \citet[p. 101]{Keynes1936} \added{also had a later, more negative view of speculation.  Here he} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd''\added{. Uninformed speculators may now dominate} and \citet{Delong1990noise} provide a model \deleted{of cases} where speculative noise provides a constraint on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

The debate about the relative merit of these two concepts of speculation continues to the current era where there has been much discussion over the role that speculation played in the boom and bust of commodities prices in the period between 2006 and 2007.  A common story that has encouraged Congressional investigation says that wild speculation drove oil and other commodities prices well above their fundamental value causing harship for commodity consumers and a subsequent collapse that was equally disruptive for the producders.  \citet{PindyckSpec} show a broad movement of commodities prices not linked to fundaments that they argue is caused by speculation.  \citet{TangSpec} suggest that this disruption was exacerbated by speculation on commodity indices.  However, \citet{ScottSpec} do not find a link between speculative positions and excess price movements in commodities and \citet{Jacksspec} documents a long history of attacks on speculation following price volatility.}

@@

\added{More recently the debate has move towards the way that noise-trading speculators may affect welfare and how that could be contained. \citet{Tobin1982} and \citet{Tobvin} developed the argument for the eponymous transaction tax that would seek to limit the influence of exchange rate speculation.  \citet{ERW} use a series of fundamentals to show how speculation casued unwarranted devaluations during the period of the European Exchange Rate Mechanism (ERM).   \citet{Tobin3} use this experience to re-state the call for a tax to reduce speculation.  However, if speculation is informed and part of the process of price discovery this tax can be counterproductive as it will reduce liquidity and may cause evengreater volatility. This is a point made by \citet{Mayer} and \citet{McKinnon}.

@@

\section{Measuring speculation}
\added{It is common practice to back market expectations out of information drawn from option prices.  This is where the expectatiosn and other information goes.  Using the risk-reversal skew is a simplified version of that.}  \footnote{If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review. }  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.
